Verifying Demonstrations

### 2018-09-03 paper/DB-anon-cred.tex
Starts writing about the l bits in DB-Schnorr

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
only \(l\) bits of the other.
The adversary now has two options.
First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
However, at this point the adversary must wait for the challenge bit 
\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
receive the correct \(r_i\) --- this relay will be detected.
The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
adversary will guess it correctly.
Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(|q|-l\) bits, for which the 
probability of success is \(2^{-(|q|-l)}\) (note that this is independent of 
the rounds).
Thus, the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)}\).

@@

\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
  complete this sentence:, our changes don't break Schnorr because ...}
Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above,
\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
shared secrets and thus assume an honest verifier, this limits the
inherent advantage of our public-key
\ac{DB} scheme.  \sonja{verifier impersonating prover: vulnerability
  we introduce against public-key DB schemes, mitigated by limiting
  size of l (bits of other s). Trade-off: want long l for reducing
  success of guessing correct sequence of challenge bits, want short l
  for reducing success of guessing the other s and finding alpha}

>>>>

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
only \(l\) bits of the other.
The adversary now has two options.
First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
However, at this point the adversary must wait for the challenge bit 
\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
receive the correct \(r_i\) --- this relay will be detected.
The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
adversary will guess it correctly.
Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
The adversary can also guess the remaining \(|q|-l\) bits, which we will 
discuss more below.
Guessing these bits is independent of the rounds and can be estimated to be 
\(2^{-(|q|-l)}\) (more details below).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)}\).

@@

Finally, it follows from the original Schnorr protocol that this is still 
\iac{PK} and \ac{ZK}.
The main concern is whether a malicious verifier can guess the remaining 
\(|q|-l\) bits after the protocol finished to compute the secret of the prover.
If we \emph{assume} that the adversary learning \(l > 0\) out of \(n\) bits is 
equivalent to the adversary learning nothing out of \(n-l\) bits, then the 
probability that the adversary succeeds is, as above, \(2^{-(|q|-l)}\).

\daniel{Not sure I follow exactly in the following.}
While the majority of \ac{DB} schemes are based on
shared secrets and thus assume an honest verifier, this limits the
inherent advantage of our public-key \ac{DB} scheme.
\sonja{verifier impersonating prover: vulnerability
  we introduce against public-key DB schemes, mitigated by limiting
  size of l (bits of other s). Trade-off: want long l for reducing
  success of guessing correct sequence of challenge bits, want short l
  for reducing success of guessing the other s and finding alpha}
